### 2020-02-25 paper/results.tex
Update paper/results.tex

For the Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ 
$3$ EFPY and then gradually decreases. This is due to the conversion of 
$^{238}$U from HALEU into fissile plutonium, which often produces the majority 
of the neutrons until the transition to Th/$^{233}$U fuel cycle. 
Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium 
isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are 
gradually depleted, during operating (the fissile material is dominated by Pu 
in these cases). For the HALEU case, the fissile material is dominated by 
$^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, 
the mass of fissile plutonium increases during operating but its value still 
relatively low. For the Pu+HALEU case, the mass of the fissile plutonium 
isotopes 
increases within the first $\approx$ $3$ EFPY and then decreases. The 
reactivity from the produced Pu is much greater than the depletion of the 
initial reactivity (due to the depletion of initial fissile isotopes), 
consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and 
then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is 
insufficient to maintain the reactor criticality and counteract neutron 
absorption in non-fissile isotopes.

>>>>

For the Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ 
$3$ EFPY and then gradually decreases. This is due to the conversion of 
$^{238}$U from HALEU into fissile plutonium, which often produces the majority 
of the neutrons until the transition to Th/$^{233}$U fuel cycle. 
Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium 
isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are 
gradually depleted, during operating (the fissile material is dominated by Pu 
in these cases). For the HALEU case, the fissile material is dominated by 
$^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, 
the mass of fissile plutonium increases during operating but its value still 
relatively low. For the Pu+HALEU case, the mass of the fissile plutonium 
isotopes 
increases within the first $\approx$ $3$ EFPY and then decreases. The 
reactivity from the produced Pu is much greater than the depletion of the 
initial reactivity (due to the depletion of initial fissile isotopes), 
consequently, $k_{eff}$ increases during the first $\approx$ $3$ EFPY and 
then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is 
insufficient to maintain the reactor criticality and counteract neutron 
absorption in non-fissile isotopes.
